\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
introduction written by Peter Loewe (shorter version of it)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64952 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Introduction}}
{
Geographical Information Systems (GIS) are known for their capacity 
to spatially enhance the capacity of management of natural resources. 
While being often used as an analytical tool, they also represent a collaborative 
scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
Thus, a large number of scientific geospatial computations depend on quality and 
correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
helps to preserve reproducibility of scientific results over time as the original author 
designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
improvements are tracked in the source code versioning system and are immediately 
available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
generation of scientists.
}

@@

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{geomorphon}
Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{geomorphon_tangible_high_tatras}
Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
\end{minipage}
}

>>>>

\hypersetup
{
    pdfauthor={Y. Chemin, V. Petras, A. Petrasova, M. Landa, S. Gebbert, P. Zambelli, M. Neteler, P. Loewe, M. Di Leo},
    pdfsubject={},
    pdftitle={GRASS GIS: a peer-reviewed scientific platform and future research repository},
    pdfkeywords={GIS, algorithms, methods, preservation, science, reproducibility}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Introduction}}
{
\setlength{\parskip}{0.3ex}

Over the last decades, GIS has become a key driver in geospatial science, research and application.
GIS software which is licensed under a free and open source software (FOSS) licence
is more than just a mere tool for spatial analysis.

GRASS GIS (Neteler et al., 2012 \cite{neteler2012grass}), a free and open source GIS,
is used by many scientists directly or as a backend in other projects
such as R or QGIS to perform geoprocessing tasks.

Thanks to the user and developer community, submitted code is evaluated
in different fields of application beyond
the field of expertise of the original authors, and different scales of magnitude
for the data to be processed.
This exceeds the established review process for scientific writing in a given journal
or a data publication in a defined field of science.

Immediate access to software repository enables instant quality checking
of the current software version both by continuous automated tests (Petras, 2014 \cite{Petras2014}),
and code review by human experts.

New scientific algorithms can be developed against the reviewed functionalities
already provided by the GRASS GIS codebase.
This avoids unnecessary overhead by re-implementation,
ensures quality by use of trusted components and allows reuse and long term preservation
within the project software repository:
Integrating scientific algorithms into GRASS GIS helps to preserve reproducibility
of scientific results over time as the original author designed it
(Rocchini \& Neteler, 2012 \cite{rocchini2012let}).
}

@@

\bigskip
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 0 0 125}, clip]{geomorphon}
Geomorphons for part of Yakima Training Center (area 5x3~km, USA)
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{geomorphon_tangible_high_tatras}
Ridges and valleys detected on the sand physical model of High Tatras (Slovakia) using \gamodule{r.geomorphon} integrated in Tangible Landscape system
\end{minipage}
}
